On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-25 Manuscript/manuscript.tex
Update

Block bootstrap is a tool to construct confidence intervals (CI) to make
inferences about dependent data. Essentially, it depends on correct estimation
of the uncertainty in the estimation, similar to the standard bootstrap
\citep{efron1979bootstrap} but for serially dependent data. Early ideas of block
bootstrap were developed not long after the startard bootstrap 
\citep{hall1985resampling, carlstein1986use,kunsch1989jackknife}. It has since
been applied in various fields, for instance, econometrics
\citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}.
Block bootstrap is especially useful for serially dependent data when the
serial dependence is not specified or not of primary interest. The method is
expected to produce CIs with coverage rates matching their nominal levels as
the sample size grows. However, when dealing with finite sample sizes, an
important question is how large the sample size must be for block bootstrap
CIs to have the desired coverage rates.

For independent data, extensive research has explored the effectiveness of
bootstrap standard errors in providing accurate uncertainty measures. For
example, \citet{hesterberg2015teachers} observes that while percentile-based
CIs for the mean parameter are more accurate than $t$-intervals for larger
sample sizes, they accuracy diminishes for smaller sample sizes. The optimal
parameter estimation of a distribution, according to
\citet{chernick2009revisiting}, depends on the sample size, the number of
bootstrap replicates, and the confidence level. In structural equation
modeling, \citet{nevitt2001performance} find that a sample size of 200--1000
is sufficient for interval estimation using standard nonparametric bootstrap.
Estimating variance component, \citet{burch2012nonparametric} report that as
the sample size increases under a normal distribution, nonparametric bootstrap
methods approach the coverage of a pivotal quantity as the sample size, but
for other distributions, the coverage can deteriorate. In estimating the
correlation coefficient of bivariate normal data, \citet{puth2015variety} note
that even for a sample size of~$100$ with true correlation coefficient~0,
bootstrap methods are less accurate than the Fisher's transformation. The
prevailing consensus highlights the necessity of a substantial sample size for
bootstrap CIs to attain the desired coverage.

@@

The goal of this paper is to provide recommendations on necessary sample size
for block bootstrap with dependent data, similar to what was done for basic
bootstrap in \citet{hesterberg2015teachers}. We consider a simple situation of
a stationary time series, where the parameters of interests are the mean,
standard deviation, and the first-order autocorrelation coefficient. We
compare six variants of block bootstrap CIs from the literature
\citep{diciccio1996bootstrap, rice2006mathematical}: a standard normal CI, and
a Student's $t$ CI, a percentile CI, a bias-corrected CI, a bias-corrected and
accelerated CI, and a recentered percentile CI proposed in this article.
Their empirical
coverage rates at different sample sizes and dependence levels are compared in
a simulation study. The results of this study suggest that recovery of
temporal dependence parameters is reliant on the type of interval used.

The remainder of the paper is organized as follows. Section~\ref{sec:bbci}
reviews block bootstrap procedures and how to use block bootstrap estimates to
construct CIs; a simple CI obtained by recentering at the point estimate is
proposed for comparison. Section~\ref{sec:simu} reports a simulation study
comparing the coverage rates of six block bootstrap CIs. A discussion
concludes in Section~\ref{sec:disc}.

@@

Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$.
Our goal is to construct a CI for a parameter $\theta$ in the data generating
model of the series. Suppose that $\hat\theta_n$ is a point estimator
of~$\theta$ based on the observed series. Bootstrap is a powerful approach to
construct CIs. If the observations in the series were independent, a standard
nonparametric bootstrap procedure would draw a large number~$B$ bootstrap
copies of the observed data, and calculate an estimate $\hat\theta_n^{(b)}$
for each copy $b = 1, \ldots, B$. The uncertainty of $\hat\theta_n$ is then
estimated by the empirical uncertainty of the $\hat\theta_n^{(b)}$'s. When
serial dependence is present, the bootstrap procedure needs to preserve the
serial dependence. Block bootstrap was motivated for this situation.

@@

Suppose that we have repeated the steps in the last subsection $B$ times, and
that for $b \in \{1, \ldots, B\}$, we have obtained an estimator
$\hat\theta_n^{(b)}$ based on the $b$th bootstrap sample using the same method
that was applied to $\{X_t: t = 1, \ldots, n\}$ to obtain $\hat\theta_n$. Now
the question is how to construct a CI for $\theta$ using the $B$ bootstrap
point estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. We
consider six kinds of block bootstrap CIs adapted from standard bootstrap CIs.

\paragraph{Standard Normal CI}
Assuming that $\hat\theta_n$ is asymptotically normally distributed with
$\theta$ as the mean, we just need an estimate of the standard error to
construct an approximate CI \citep[p.168]{efron1993introduction}. Let
$\widehat{\text{SE}}$ be the empirical standard error of the block bootstrap
copies of $\hat\theta_n^{(b)}$, $b = 1, \ldots, B$. Let $z_{(\alpha)}$ be the
upper $\alpha$ quantile of the standard normal distribution. A
$(1 - \alpha)100\%$ standard normal CI is
\[
(\hat{\theta}_{n} - z_{(1-\alpha/2)}\widehat{\text{SE}}, \quad
\hat{\theta}_{n} - z_{(\alpha/2)}\widehat{\text{SE}}).
\]
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric. The
Standard CI is a table-based bootstrap interval approach. Its validity relies
on whether the distribution of $\hat\theta_n$ is reasonably well approximated
by its asymptotic normal distribution and whether the bootstrap
$\widehat{\text{SE}}$ approximates the true standard error.

\paragraph{Student's $t$ CI}
The procedure for constructing a Student's $t$ CI based on standard bootstrap
is described in \citet[p.158]{efron1993introduction}. Let $t_{(\alpha, k)}$ be
the upper $\alpha$ quantile of a $t$ distribution with $k$ degrees of freedom.
With block bootstrapping, a $(1 - \alpha)100\%$ Student's $t$ CI is
\[
(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\hat{\text{SE}}, \quad
\hat{\theta}_{n} - t_{(\alpha/2), k -1}\hat{\text{SE}}),
\]
%\eds{define $t_{(.)}$ and check the signs}  \mc{addressed}
where $k$ is the number of blocks. This CI is centered by the point estimator
$\hat\theta_n$ and is symmetric. Like the standard normal interval, the
Student's $t$ CI is a table-based bootstrap interval approach. In this case,
its validity relies on whether the distribution of $\hat\theta_n$ is
reasonably well approximation by the $t_{k-1}$ distribution with an expected
value of $\theta$, and whether the bootstrap $\widehat{\text{SE}}$
approximates the true standard error.

\paragraph{Percentile CI}
The percentile CI was first suggested in \citet{efron1979bootstrap}.
\jy{The previous superscript does not make sense because
  $b \in \{1, \ldots,  B\}$. Make similar changes to other places as needed.}
Let $\hat\theta_{n, \alpha}^B$ be the empirical $100\alpha$th percentile of
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. The $(1 - \alpha)100\%$
empirical percentile CI is
\[
(\hat\theta_{n, \alpha/2}^{(b)}, \quad \hat\theta_{n, 1 - \alpha/2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$. As
will be shown in our simulation study, this approach works well for the
marginal mean and standard deviation of a serially dependent process, but its
coverage of the temporal dependence deteriorates as $n$ increases, which is
contrary to what one would expect.

\paragraph{Bias Corrected (BC) CI}
The procedure for constructing a Bias Corrected Bootstrap CI based on standard
bootstrap is described in \citet{carpenter2000bootstrap}. Let
$b = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
$b \in \{1, \ldots, B\}$. Define $\alpha_1 = \Phi(2b - z_{\alpha/2})$ and 
$\alpha_2 = \Phi(2b - z_{1 - \alpha/2})$. A $(1 - \alpha)100\%~BC$ CI is
\[
(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
\]

\paragraph{Bias Corrected and Accelerated (BCA) CI}
The BCA CI was first suggested in \citet{efron1987better}. Let
$\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
$b \in \{1, \ldots, B\}$. Let $Z_{(i)}$ be the original sample without the
$i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let $\hat{\theta}_{(i)}$ be
the statistic of $Z_{(i)}$, and let
$\hat{\theta}_{(.)} = \sum_{i=1}^{k} \hat{\theta}_{(i)} / k$. 
Let 
\[
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}.
\]
Define
\[
\alpha_1 = \Phi\left(z_0 + \frac{z_{0} +
  z_{\alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{\alpha/2})}\right)
\text{ and }
\alpha_2 = \Phi\left(z_0 + \frac{z_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{1 - \alpha/2})}\right).
\]
A $(1 - \alpha)100\%~BC_a$ CI is
\[
(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
BCA method corrects for bias and skewness of the $B$ bootstrap point
estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
bias-correction and acceleration factors. The acceleration factor refers to
the rate of change of the standard error of $\hat\theta_n$ with respect to
$\theta$.

@@

We propose a CI that is centered at the point estimator and uses the variation
in the bootstrap estimates to construct the error bound. This interval requires
\jy{Note the notation change and do a thorough check}
the computation of
$\bar\theta_n^B = n^{-1}\sum_{b=1}^B \hat\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$. A
$(1 - \alpha)100\%$ CI is
\[
(\hat\theta_{n, \alpha/2}^{(b)} - \widehat{\text{bias}}, \quad
\hat\theta_{n, 1 - \alpha/2}^{(b)} - \widehat{\text{bias}}).
\]
This CI is centered around $\hat\theta_n$ and can also be rewritten
as 
\[
(\hat\theta_n + \hat\theta_{n, \alpha/2}^{(b)} - \bar\theta_n^{(b)}, \quad
\hat\theta_n + \hat\theta_{n, 1 - \alpha/2}^{(b)} - \bar\theta_n^{(b)}).
\]
It is not necessarily symmetric, as different critical values are used to compute
the lower and upper bounds. It has the same width as the Percentile CI.

@@

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x = 1$, the standard deviation of $X_t$; and
3) $\phi$, the lag-1 auto-correlation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we
generated 10000 replicates. For each replicate, we constructed seven 95\% block
bootstrap CIs for each parameter as described in the last section. We can
estimate $\mu$, $\sigma_x$, and $\phi$ by computing the sample mean, sample 
standard deviation, and lag-1 auto-correlation, respectively, of each
bootstrap sample, and then construct intervals for each parameter using the
appropriate procedures described in Section~\ref{sec:bbci}. Then we estimated
their actual coverage rates along with their 95\% confidence intervals from
the 10000 replicates. The block bootstrap sampling step was done with function
\texttt{tsboot} from R package \textsl{boot} \citep{boot}, with block size
$\lceil n / l \rceil$. This function by default is an implementation of moving
block bootstrap as described in the previous section, meaning that that blocks
are allowed to wrap around, and $l = \lceil n^{1/3} \rceil$.

@@

For estimating the mean parameter~$\mu$, Figure~\ref{fig:mu} suggests that all
methods eventually approach correct coverage of $\mu$ as sample size
increases. Student's $t$ CIs appear to need the smallest sample size
to achieve correct coverage, except for samples with strong negative
dependence, in which case, they actually over-cover $\mu$ for smaller sample
sizes. For instance, for a sample with $n = 100$ and $\phi = -0.4$, the lower
bound for a Students $t$ CIs coverage of $\mu$ is greater than 95\%, whereas
the coverage intervals for other methods contain 95\%. The standard,
percentile, BC, and BCA, and recentered percentile CIs require similar sample
sizes to recover $\mu$ at the nominal level for all combinations of $n$ and
$\phi$. All methods seem to require a smaller sample to recover $\mu$ at the
nominal rate when dealing with negative dependence versus positive dependence.
For example, BC CIs recover $\mu$ for $n \geq 100$ when $\phi = -0.2$, but
they only recover $\mu$ for $n \geq 800$ when $\phi = 0.2$. In addition, as a
negative dependence gets stronger, holding everything else equal, coverage
increases, which lead to the Student $t$ CI's aforementioned over-coverage. As
a positive dependence gets stronger, holding everything else equal, coverage
decreases, and a larger sample is necessary to recover~$\mu$.

For estimating the standard deviation parameter~$\sigma_x$,
Figure~\ref{fig:sigma} suggests that every method can reach nominal coverage of
$\sigma_x$ if the sample is large enough, but for a given $n$ and $\phi$,
coverage of $\sigma_x$ will be lower than coverage of $\mu$ in general. Like
$\mu$, $\sigma_x$ can be covered by Student $t$ CIs with smaller sample sizes
when compared to other methods. Unlike $\mu$, there is no over-coverage issue for
$\sigma$ when $\phi = -0.4$. Standard, percentile, BC, BCA, and recentered percentile
CIs again have similar performance. All methods seem to have slightly higher
coverage of $\sigma_x$ when $\phi$ is negative versus when $\phi$ is positive.
Regardless of the sign, coverage of $\sigma_x$ gets worse as the strength of
the temporal dependence increases.
\jy{Compared to Figure 1, there is no over-coverage in this case. Say someting
  about this observation.} \mc{addressed}

For estimating the auto-correlation parameter~$\phi$, Figure~\ref{fig:phi}
suggests that while standard, Student's $t$, and recentered percentile CIs do
approach correct coverage as sample size increases, Percentile, BC, and
BCA CIs deteriorate as sample size increases, especially as the strength of
the temporal dependence increases. Because of this, only Standard, Student's
$t$, and recentered percentile CIs should be considered as effective block bootstrap
methods to estimate $\phi$. Student's $t$ CIs once again can achieve correct
coverage with smaller sample sizes when compared to standard and recentered percentile CIs
which perform similarly. Student's $t$ CIs can can recover $\phi$ at the
nominal level for $n \geq 100$ when the sample's temporal dependence is as
strong as 0.4. Coverage appears to be higher for all methods when the
dependence is negative rather than positive. Whether or not the dependence is
negative or positive, coverage of $\phi$ seems to increase slightly as the
absolute value increases for standard, Student's $t$, and recentereed percentile
CIs. For the values of $\phi$ observed, there are no examples
of over-coverage for standard, Student's $t$, BC, BCA, or recentered percentile CIs.
However, Percentile CIs appear to over-cover $\phi$ for smaller sample sizes when 
$\phi = -0.2$ and when $\phi = 0$, indicating again that they should not be used.

\jy{check for no uppercases for recentered percentile, etc. throughout}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/norm_phi_intervals}
  \caption{50 replicate percentile, BC, and recentered percentile
    CIs for samples of $n \in \{800, 1600\}$ for an AR(1) process with
    $\phi = 0.4$. For each replicate, the lower and upper bounds of the CIs
    are displayed, as well as $\hat\theta_n$ (blue circle) and
    $\bar\theta_n^{(b)}$ (red cross). }
  \label{fig:npi}
\end{figure}

\jy{The red cross is not $\theta_n^{(b)}$, but their average over
  $b = 1,  \ldots, B$. Define this as bootstrap point estimate in section 2.2
  for ease of referencing in the discussion.}

\jy{Keep the interval labels consistent in figure and in the text}

>>>>

Block bootstrap is a tool to construct confidence intervals (CI) to make
inferences about dependent data. Essentially, it depends on correct estimation
of the uncertainty in the estimation, similar to the standard bootstrap
\citep{efron1979bootstrap} but for serially dependent data. Early ideas of block
bootstrap were developed not long after the standard bootstrap 
\citep{hall1985resampling, carlstein1986use,kunsch1989jackknife}. It has since
been applied in various fields, for instance, econometrics
\citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}.
Block bootstrap is especially useful for serially dependent data when the serial 
dependence is not specified or not of primary interest. The method is expected 
to produce CIs with coverage rates matching their nominal levels as the sample 
size grows. However, when dealing with finite sample sizes, an important 
question is how large the sample size must be for block bootstrap CIs to have 
the desired coverage rates.

For independent data, extensive research has explored the effectiveness of
bootstrap standard errors in providing accurate uncertainty measures. For 
example, \citet{hesterberg2015teachers} observes that while percentile-based CIs 
for the mean parameter are more accurate than $t$-intervals for larger sample 
sizes, their accuracy diminishes for smaller sample sizes. The optimal parameter 
estimation of a distribution, according to \citet{chernick2009revisiting}, 
depends on the sample size, the number of bootstrap replicates, and the 
confidence level. In structural equation modeling, \citet{nevitt2001performance} 
find that a sample size of 200--1000 is sufficient for interval estimation using 
standard nonparametric bootstrap. In estimating variance components, 
\citet{burch2012nonparametric} reports that as the sample size increases under a 
normal distribution, nonparametric bootstrap methods approach the coverage of a 
pivotal quantity, but for other distributions, the coverage can deteriorate. In 
estimating the correlation coefficient of bivariate normal data, 
\citet{puth2015variety} note that even for a sample size of~$100$ with true 
correlation coefficient~0, bootstrap methods are less accurate than the Fisher's 
transformation. The prevailing consensus highlights the necessity of a 
substantial sample size for bootstrap CIs to attain the desired coverage.

@@

The goal of this paper is to provide recommendations on necessary sample size 
for block bootstrap with dependent data, similar to what was done for basic 
bootstrap in \citet{hesterberg2015teachers}. We consider a simple situation of 
a stationary time series, where the parameters of interests are the mean, 
standard deviation, and the first-order autocorrelation coefficient. We compare 
six variants of block bootstrap CIs from the literature
\citep{diciccio1996bootstrap, rice2006mathematical}: a standard normal CI, a 
Student's $t$ CI, a percentile CI, a bias-corrected CI, a bias-corrected and 
accelerated CI, and a recentered percentile CI proposed in this article. Their 
empirical coverage rates at different sample sizes and dependence levels are 
compared in a simulation study. The results of this study suggest that recovery 
of temporal dependence parameters is reliant on the type of interval used.

The remainder of the paper is organized as follows. Section~\ref{sec:bbci} 
reviews block bootstrap procedures and how to use block bootstrap estimates to
construct CIs; a simple CI obtained by recentering at the original point 
estimate is proposed for comparison. Section~\ref{sec:simu} reports a simulation 
study comparing the coverage rates of six block bootstrap CIs. A discussion
concludes in Section~\ref{sec:disc}.

@@

Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$. 
Our goal is to construct a CI for a parameter $\theta$ in the data generating 
model of the series. Suppose that $\hat\theta_n$ is a point estimator 
of~$\theta$ based on the observed series. Bootstrap is a powerful approach to
construct CIs. If the observations in the series were independent, a standard
nonparametric bootstrap procedure would draw a large number~$B$ bootstrap copies 
of the observed data, and calculate a bootstrap point estimate 
$\hat\theta_n^{(b)}$ for each copy $b = 1, \ldots, B$. The uncertainty of 
$\hat\theta_n$ is then estimated by the empirical uncertainty of the bootstrap 
point estimates. When serial dependence is present, the bootstrap procedure 
needs to preserve the serial dependence. Block bootstrap was motivated for this 
situation.

@@

Suppose that we have repeated the steps in the last subsection $B$ times, and
that for $b \in \{1, \ldots, B\}$, we have obtained a bootstrap point estimate
$\hat\theta_n^{(b)}$ based on the $b$th bootstrap sample using the same method
that was applied to $\{X_t: t = 1, \ldots, n\}$ to obtain $\hat\theta_n$. Now
the question is how to construct a CI for $\theta$ using the $B$ bootstrap point 
estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. We consider six 
kinds of block bootstrap CIs adapted from standard bootstrap CIs.

\paragraph{Standard Normal CI}
Assuming that $\hat\theta_n$ is asymptotically normally distributed with 
$\theta$ as the mean, we just need an estimate of the standard error to 
construct an approximate CI \citep[p.168]{efron1993introduction}. Let
$\widehat{\text{SE}}$ be the empirical standard error of the bootstrap point 
estimates $\hat\theta_n^{(b)}$ for $b \in \{1, \ldots, B\}$. Let $z_{(\alpha)}$ 
be the upper $\alpha$ quantile of the standard normal distribution. 
A $(1 - \alpha)100\%$ standard normal CI is
\[
(\hat{\theta}_{n} - z_{(1-\alpha/2)}\widehat{\text{SE}}, \quad
\hat{\theta}_{n} - z_{(\alpha/2)}\widehat{\text{SE}}).
\]
This CI is centered by the original point estimate $\hat\theta_n$ and is 
symmetric. The standard CI is a table-based bootstrap interval approach. Its 
validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
approximated by its asymptotic normal distribution and whether the bootstrap
$\widehat{\text{SE}}$ approximates the true standard error.

\paragraph{Student's $t$ CI}
The procedure for constructing a Student's $t$ CI based on standard bootstrap is 
described in \citet[p.158]{efron1993introduction}. Let $t_{(\alpha, k)}$ be the 
upper $\alpha$ quantile of a $t$ distribution with $k$ degrees of freedom. With 
block bootstrapping, 
a $(1 - \alpha)100\%$ Student's $t$ CI is
\[
(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\widehat{\text{SE}}, \quad
\hat{\theta}_{n} - t_{(\alpha/2), k -1}\widehat{\text{SE}}),
\]
%\eds{define $t_{(.)}$ and check the signs}  \mc{addressed}
where $k$ is the number of blocks. This CI is centered by the original point 
estimate $\hat\theta_n$ and is symmetric. Like the standard normal interval, the
Student's $t$ CI is a table-based bootstrap interval approach. In this case, its 
validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
approximated by the $t_{k-1}$ distribution with an expected value of $\theta$ 
and whether the bootstrap $\widehat{\text{SE}}$ approximates the true standard 
error.

\paragraph{Percentile CI}
The percentile CI was first suggested in \citet{efron1979bootstrap}.
\jy{The previous superscript does not make sense because
  $b \in \{1, \ldots,  B\}$. Make similar changes to other places as needed.} 
\mc{addressed}
Let $\hat\theta_{n, \alpha}^B$ be the empirical $100\alpha$th percentile of
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. 
A $(1 - \alpha)100\%$ empirical percentile CI is
\[
(\hat\theta_{n, \alpha/2}^{B}, \quad \hat\theta_{n, 1 - \alpha/2}^{B}).
\]
This CI is not necessarily centered by the original point estimate 
$\hat\theta_n$. As will be shown in our simulation study, this approach works 
well for the marginal mean and standard deviation of a serially dependent 
process, but its coverage of the temporal dependence deteriorates as $n$ 
increases, which is contrary to what one would expect.

\paragraph{Bias-Corrected (BC) CI}
The procedure for constructing a bias-corrected Bootstrap CI based on standard
bootstrap is described in \citet{carpenter2000bootstrap}. Let
$b = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
$b \in \{1, \ldots, B\}$. Define $\alpha_1 = \Phi(2b - z_{\alpha/2})$ and 
$\alpha_2 = \Phi(2b - z_{1 - \alpha/2})$. 
A $(1 - \alpha)100\%$ ~BC CI is
\[
(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
\]

\paragraph{Bias-Corrected and Accelerated (BCA) CI}
The BCA CI was first suggested in \citet{efron1987better}. Let
$\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
$b \in \{1, \ldots, B\}$. Let $Z_{(i)}$ be the original sample without the
$i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let $\hat{\theta}_{(i)}$ be the 
statistic of $Z_{(i)}$, and let
$\hat{\theta}_{(.)} = k^{-1}\sum_{i=1}^{k} \hat{\theta}_{(i)}$. 
Let 
\[
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}.
\]
Define
\[
\alpha_1 = \Phi\left(z_0 + \frac{z_{0} +
  z_{\alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{\alpha/2})}\right)
\text{ and }
\alpha_2 = \Phi\left(z_0 + \frac{z_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{1 - \alpha/2})}\right).
\]
A $(1 - \alpha)100\%$ ~BCA CI is
\[
(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
\]
This CI is not necessarily centered by $\hat\theta_n$. The BCA method corrects 
for bias and skewness of the $B$ bootstrap point estimates 
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including 
bias-correction and acceleration factors. The acceleration factor refers to the 
rate of change of the standard error of $\hat\theta_n$ with respect to $\theta$.

@@

We propose a CI that is centered at the original point estimate and uses the 
variation in the bootstrap estimates to construct the error bound. This interval 
requires
\jy{Note the notation change and do a thorough check} \mc{addressed}
the computation of $\bar\theta_n^B = n^{-1}\sum_{b=1}^B \hat\theta_n^{(b)}$, the 
mean of all bootstrap point estimates, and 
$\widehat{\text{bias}} = \bar\theta_n^{B} - \hat\theta_n$. 
A $(1 - \alpha)100\%$ CI is
\[
(\hat\theta_{n, \alpha/2}^{B} - \widehat{\text{bias}}, \quad
\hat\theta_{n, 1 - \alpha/2}^{B} - \widehat{\text{bias}}).
\]
This CI is centered around $\hat\theta_n$ and can also be rewritten as 
\[
(\hat\theta_n + \hat\theta_{n, \alpha/2}^{B} - \bar\theta_n^{B}, \quad
\hat\theta_n + \hat\theta_{n, 1 - \alpha/2}^{B} - \bar\theta_n^{B}).
\]
It is not necessarily symmetric, as different critical values are used to 
compute the lower and upper bounds. It has the same width as the percentile CI.

@@

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x = 1$, the standard deviation of $X_t$; and
3) $\phi$, the lag-1 auto-correlation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 
10000 replicates. For each replicate, we constructed six 95\% block bootstrap 
CIs for each parameter as described in the last section. We can estimate $\mu$, 
$\sigma_x$, and $\phi$ by computing the sample mean, sample standard deviation, 
and lag-1 auto-correlation, respectively, of each bootstrap sample. Then we can 
construct intervals for each parameter using the appropriate procedures 
described in Section~\ref{sec:bbci}. Then we estimated their actual coverage 
rates along with their 95\% confidence intervals from the 10000 replicates. The 
block bootstrap sampling step was done with function \texttt{tsboot} from R 
package \textsl{boot} \citep{boot}, with block size $\lceil n / l \rceil$. This 
function by default is an implementation of moving block bootstrap as described 
in the previous section, meaning that that blocks are allowed to wrap around, 
and $l = \lceil n^{1/3} \rceil$.

@@

For estimating the mean parameter~$\mu$, Figure~\ref{fig:mu} suggests that all
methods eventually approach correct coverage of $\mu$ as sample size increases. 
Student's $t$ CIs appear to need the smallest sample size to achieve correct 
coverage, except for samples with strong negative dependence, in which case, 
they actually over-cover $\mu$ for smaller sample sizes. For instance, for a 
sample with $n = 100$ and $\phi = -0.4$, the lower bound for a Students $t$ CI's 
coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for other 
methods contain 95\%. The standard, percentile, BC, and BCA, and recentered 
percentile CIs require similar sample sizes to recover $\mu$ at the nominal 
level for all combinations of $n$ and $\phi$. All methods seem to require a 
smaller sample to recover $\mu$ at the nominal rate when dealing with negative 
dependence versus positive dependence. For example, BC CIs recover $\mu$ for 
$n \geq 100$ when $\phi = -0.2$, but they only recover $\mu$ for $n \geq 800$ 
when $\phi = 0.2$. In addition, as a negative dependence gets stronger, holding 
everything else equal, coverage increases, which lead to the Student $t$ CI's 
aforementioned over-coverage. As a positive dependence gets stronger, holding 
everything else equal, coverage decreases, and a larger sample is necessary to 
recover~$\mu$.

For estimating the standard deviation parameter~$\sigma_x$,
Figure~\ref{fig:sigma} suggests that every method can reach nominal coverage of
$\sigma_x$ if the sample is large enough, but for a given $n$ and $\phi$,
coverage of $\sigma_x$ will be lower than coverage of $\mu$ in general. Like 
$\mu$, $\sigma_x$ can be covered by Student $t$ CIs with smaller sample sizes
when compared to other methods. Unlike $\mu$, there is no over-coverage issue 
for $\sigma_x$ when $\phi = -0.4$. Standard, percentile, BC, BCA, and recentered 
percentile CIs again have similar performance. All methods seem to have slightly 
higher coverage of $\sigma_x$ when $\phi$ is negative versus when $\phi$ is 
positive. Regardless of the sign, coverage of $\sigma_x$ gets worse as the 
strength of the temporal dependence increases.
\jy{Compared to Figure 1, there is no over-coverage in this case. Say something
  about this observation.} \mc{addressed}

For estimating the auto-correlation parameter~$\phi$, Figure~\ref{fig:phi}
suggests that while standard, Student's $t$, and recentered percentile CIs do
approach correct coverage as sample size increases, percentile, BC, and BCA CIs 
deteriorate as sample size increases, especially as the strength of the temporal 
dependence increases. Because of this, only standard, Student's $t$, and 
recentered percentile CIs should be considered as effective block bootstrap 
methods to estimate $\phi$. Student's $t$ CIs once again can achieve correct
coverage with smaller sample sizes when compared to standard and recentered 
percentile CIs which perform similarly. Student's $t$ CIs can can recover $\phi$ 
at the nominal level for $n \geq 100$ when the sample's temporal dependence is 
as strong as 0.4. Coverage appears to be higher for all methods when the
dependence is negative rather than positive. Whether or not the dependence is
negative or positive, coverage of $\phi$ seems to increase slightly as the
absolute value increases for standard, Student's $t$, and recentered percentile
CIs. For the values of $\phi$ observed, there are no examples of over-coverage 
for standard, Student's $t$, BC, BCA, or recentered percentile CIs. However, 
percentile CIs appear to over-cover $\phi$ for smaller sample sizes when 
$\phi = -0.2$ and when $\phi = 0$, indicating again that they should not be used.

\jy{check for no uppercases for recentered percentile, etc. throughout}
\mc{addressed}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/norm_phi_intervals}
  \caption{50 replicate percentile, BC, and recentered percentile CIs for 
    samples of $n \in \{800, 1600\}$ for an AR(1) process with $\phi = 0.4$. For 
    each replicate, the lower and upper bounds of the CIs are displayed, as well 
    as $\hat\theta_n$ (blue circle) and $\bar\theta_n^{B}$ (red cross).}
  \label{fig:npi}
\end{figure}

\jy{The red cross is not $\theta_n^{(b)}$, but their average over
  $b = 1,  \ldots, B$. Define this as bootstrap point estimate in section 2.2
  for ease of referencing in the discussion.}
\mc{I'm not sure if I addressed this like you intended, I defined 
$\hat\theta_n^{(b)}$ as bootstrap point estimate, and referred to 
$\hat\theta_n$ as the original point estimate. Did you want me to define
$\bar\theta_n^{B}$ as the bootstrap point estimate?}

\jy{Keep the interval labels consistent in figure and in the text}
\mc{is it fine to have them capitalized in the figures?}

The outcomes of the $\phi$ estimation raise a natural question about the 
lackluster performance of certain methodologies. To delve into this inquiry, a
set of 50 CIs was generated for each of the percentile, BC, and recentered
percentile  approaches for samples of $n \in \{800, 1600\}$. Illustrated in 
Figure~\ref{fig:npi}, it becomes evident that the percentile-based CIs exhibit a 
notable bias, predominantly manifesting as a substantial underestimation of 
$\phi$ with point estimator $\bar\theta_n^B$, that is, the average of $B$ 
bootstrap point estimates. As the sample size increases from 800 to 1600, this 
bias does not vanish while the uncertainty reduces, which explains why the 
coverage rates deteriorate. The bias in $\bar\theta_n^B$ also appears to 
invalidate the bias-correction in the BC bootstrap, leading to the poor 
performance of the BC intervals. The BCA intervals have the same problem as the 
BC intervals in the bias-correction step. The root of the issue appears to be 
that the autocorrelation in the block bootstrap samples is somehow smaller 
compared to that in the original sample. On the other hand, the original point 
estimate $\hat\theta_n$ is asymptotically unbiased. Since the width is based on 
the uncertainty in the bootstrap point estimates $\hat\theta_n^{(b)}$, 
$b = 1, \ldots, B$, the percentile CIs recentered at the original point estimate 
provide desired coverage.
